The SMT Competition 2015--2018

### 2018-10-19 2018/report/SMT-COMP.tex
Distribution of benchmarks by file size

\usepackage{pifont}
\usepackage{comment}
\usepackage{multirow}

@@

All problems used in the SMT Competition come from the SMT Library
(SMT-LIB).  This is a large collection of benchmark problems from
various sources.  The SMT Library is available from a public
repository~\cite{smtlib-repository}, and each new release is mirrored
on StarExec, the cluster on which the competition runs.  Users of SMT
solvers are encouraged to submit new and interesting benchmarks to the
library, which has grown from 1,352 benchmarks in 2005~\cite{BdMS05}
to 347,011 benchmarks in 2018.

@@

The SMT Library classifies benchmarks according to their \emph{logic},
that is, according to the specific combination of background theories
that the benchmark uses.  Logic names are composed of letter groups
that refer to these background theories: {\tt A} or {\tt AX} for the
theory of arrays, {\tt BV} for the theory of bit-vectors, {\tt DT} for
algebraic datatypes, {\tt FP} for the floating-point theory, {\tt IA}
for integer arithmetic, {\tt RA} for real arithmetic, {\tt IRA} for
mixed integer and real arithmetic, {\tt S} for the theory of strings,
{\tt UF} for uninterpreted functions (i.e., free symbols).
Additionally, logics may impose further syntactic restrictions, such
as the absence of quantifiers ({\tt QF}), the restriction to
difference logic over the integers ({\tt IDL}) or reals ({\tt RDL}),
or to the (non-)linear fragment of arithmetic ({\tt L} or {\tt N},
respectively, before {\tt IA}, {\tt RA} or {\tt IRA}).  For instance,
the logic {\tt QF\_UFLIA} contains quantifier-free formulas with
uninterpreted functions over linear integer arithmetic.  These
restrictions are typically motivated by the existence of efficient
decision procedures for certain syntactic fragments.

@@

The 2018 release of the SMT Library contained 336,844 non-incremental
benchmarks in 51 logics, as well as~10,167 incremental benchmarks
(with a total of nearly 32 million {\tt check-sat} commands) in 26
logics.  Table~\ref{table:smtlib} presents further data on the size of
the SMT Library since~2015.  While the library usually grows from one
year to the next because of the inclusion of new benchmarks and
logics, continuous curation efforts may also cause benchmarks to be
removed or reclassified on occasion, thereby causing individual logics
or even the entire library to shrink.  From 2015--2018, the total
number of benchmarks has increased by 68\,\%.
Figure~\ref{fig:benchmark-sizes} shows how the file size of individual
benchmarks is distributed.  The largest benchmark in the 2018 release
has a size of 993~MiB; the total size of the library is 85~GiB.

@@

\begin{figure}
  \TODO \\
  \TODO \\
  \TODO \\
  \TODO \\
  \TODO \\
  \TODO \\
  \TODO \\

  \caption{Distribution of benchmark sizes in the SMT Library (2018).}
  \label{fig:benchmark-sizes}
\end{figure}

@@

Tables~\ref{table:benchmarks-main-track}--\ref{table:benchmarks-unsat-core-track}
show the number of benchmarks that were used in each competition track
and division since 2015.  A dash indicates that no eligible benchmarks
were available, and hence the corresponding SMT-LIB logic was not
actually a competition division in that track and year.

\begin{table}
  \caption{Number of benchmarks used in the main track (by division)}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.83]{\begin{tabular}{|l|r|r|r|r|}
    \hline
    Division & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    ABVFP      &     -- &     -- &      1 &     1 \\
    ALIA       &     42 &     42 &     42 &    42 \\
    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
    AUFDTLIA   &     -- &     -- &    728 &   728 \\
    AUFLIA     &      4 &      4 &      4 &     4 \\
    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
    BV         &     85 &     85 &   5151 &  5751 \\
    BVFP       &     -- &     -- &     24 &    24 \\
    FP         &     -- &     -- &     61 &    61 \\
    LIA        &    201 &    201 &    388 &   388 \\
    LRA        &    339 &    339 &   2419 &  2419 \\
    NIA        &      9 &      9 &     14 &    14 \\
    NRA        &   3788 &   3788 &   3811 &  3813 \\
    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
    QF\_ALIA   &    134 &    139 &    139 &   139 \\
    QF\_ANIA   &      6 &      8 &      8 &     8 \\
    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
    QF\_AX     &    551 &    551 &    551 &   551 \\
    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
    QF\_DT     &     -- &     -- &   8000 &  8000 \\
    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
    QF\_LIRA   &      6 &      6 &      7 &     7 \\
    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
    QF\_NIRA   &      2 &      2 &      3 &     3 \\
    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
    QF\_RDL    &    220 &    220 &    255 &   255 \\
    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
    UF         &   2839 &   2839 &   7562 &  7562 \\
    UFBV       &     71 &     71 &    200 &   200 \\
    UFDT       &     -- &     -- &   4535 &  4527 \\
    UFDTLIA    &     -- &     -- &    303 &   303 \\
    UFIDL      &     68 &     68 &     68 &    68 \\
    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
    UFLRA      &     25 &     25 &     15 &    15 \\
    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
    \hline
    Total      & 154238 & 154424 & 256973 & 333241 \\
    \hline
  \end{tabular}}
\end{table}

@@

>>>>

\usepackage{pifont}
\usepackage{comment}
\usepackage{multirow}
\usepackage{tikz}

@@

All problems used in the SMT Competition come from the SMT Library
(SMT-LIB).  This is a large collection of benchmark problems from
various sources.  The SMT Library is available from a public
repository~\cite{smtlib-repository}, and each new release is mirrored
on StarExec, the cluster on which the competition runs.  Users of SMT
solvers are encouraged to submit new and interesting benchmarks to the
library, which has grown from 1,352 benchmarks in~2005~\cite{BdMS05}
to 347,011 benchmarks in 2018.

@@

The SMT Library classifies benchmarks according to their \emph{logic},
that is, according to the specific combination of background theories
that the benchmark uses.  Logic names are composed of letter groups
that refer to these background theories: {A} or {AX} for the theory of
arrays, {BV} for the theory of bit-vectors, {DT} for algebraic
datatypes, {FP} for the floating-point theory, {IA} for integer
arithmetic, {RA} for real arithmetic, {IRA} for mixed integer and real
arithmetic, {S} for the theory of strings, {UF} for uninterpreted
functions (i.e., free symbols).  Additionally, logics may impose
further syntactic restrictions, such as the absence of quantifiers
({QF\_}), the restriction to difference logic over the
integers~({IDL}) or reals ({RDL}), or to the (non-)linear fragment of
arithmetic ({L} or {N}, respectively, before {IA}, {RA} or {IRA}).
For instance, the logic QF\_UFLIA contains quantifier-free formulas
with uninterpreted functions over linear integer arithmetic.  These
restrictions are typically motivated by the existence of efficient
decision procedures for certain syntactic fragments.

@@

The 2018 release of the SMT Library contained 336,844 non-incremental
benchmarks in 51 logics, as well as~10,167 incremental benchmarks
(with a total of nearly 32 million {\tt check-sat} commands) in 26
logics.  Table~\ref{table:smtlib} presents further data on the size of
the SMT Library since~2015.  While the library usually grows from one
year to the next because of the inclusion of new benchmarks and
logics, continuous curation efforts may also cause benchmarks to be
removed or reclassified on occasion, thereby causing individual logics
or even the entire library to shrink.  From~2015 to~2018, the total
number of benchmarks has increased by~68\,\%.
Figure~\ref{fig:benchmark-sizes} shows how the file size of individual
benchmarks is distributed.  The largest benchmark in the 2018 release
had a size of 1,041~MB; the total size of the release was 91~GB.

@@

\begin{figure}
  \centering
  \scalebox{.96}[.96]{\begin{tikzpicture}
    \draw [gray] (0,0) -- (14,0);
    \draw [gray] (0,.9) -- (14,.9);
    \draw [gray] (0,1.8) -- (14,1.8);
    \draw [gray] (0,2.7) -- (14,2.7);
    \draw [gray] (0,3.6) -- (14,3.6);
    \draw [gray] (0,4.5) -- (14,4.5);
    \draw [gray] (0,5.4) -- (14,5.4);

    \node [left] at (0,0) {\footnotesize 0};
    \node [left] at (0,.9) {\footnotesize 1};
    \node [left] at (0,1.8) {\footnotesize 10};
    \node [left] at (0,2.7) {\footnotesize 100};
    \node [left] at (0,3.6) {\footnotesize 1000};
    \node [left] at (0,4.5) {\footnotesize 10000};
    \node [left] at (0,5.4) {\footnotesize 100000};

    \node [rotate=90] at (-1.5,2.7) {\small Number of benchmarks};

    \draw [fill=black] (0.5,0) rectangle (1.5,5.1630077857); % 54535
    \draw [fill=black] (2.25,0) rectangle (3.25,5.5885514492); % 161995
    \draw [fill=black] (4,0) rectangle (5,5.3624537158); % 90841
    \draw [fill=black] (5.75,0) rectangle (6.75,4.9369959734); % 30588
    \draw [fill=black] (7.5,0) rectangle (8.5,4.4297518088); % 8355
    \draw [fill=black] (9.25,0) rectangle (10.25,3.3931037653); % 589
    \draw [fill=black] (11,0) rectangle (12,2.7264453999); % 107
    \draw [fill=black] (12.75,0) rectangle (13.75,0.9); % 1

    \node [below] at (1,0) {\footnotesize $[10^2, 10^3[$};
    \node [below] at (2.75,0) {\footnotesize $[10^3, 10^4[$};
    \node [below] at (4.5,0) {\footnotesize $[10^4, 10^5[$};
    \node [below] at (6.25,0) {\footnotesize $[10^5, 10^6[$};
    \node [below] at (8,0) {\footnotesize $[10^6, 10^7[$};
    \node [below] at (9.75,0) {\footnotesize $[10^7, 10^8[$};
    \node [below] at (11.5,0) {\footnotesize $[10^8, 10^9[$};
    \node [below] at (13.25,0) {\footnotesize $[10^9, 10^{10}[$};

    \node [] at (7,-1) {\small File size in bytes};
  \end{tikzpicture}}
  \caption{Distribution of SMT-LIB benchmarks by file size (2018).}
  \label{fig:benchmark-sizes}
\end{figure}

@@

Tables~\ref{table:benchmarks-main-track}--\ref{table:benchmarks-unsat-core-track}
show the number of benchmarks that were used in each competition track
and division since~2015.  A dash indicates that no eligible benchmarks
were available, and hence the corresponding SMT-LIB logic was not
actually a competition division in that track and year.  The size of
divisions varies widely, from just one benchmark in ABVFP to~72,705
benchmarks in QF\_SLIA.

\begin{table}
  \caption{Number of benchmarks used in the main track (by division)}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.82]{\begin{tabular}{|l|r|r|r|r|}
    \hline
    Division & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    ABVFP      &     -- &     -- &      1 &     1 \\
    ALIA       &     42 &     42 &     42 &    42 \\
    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
    AUFDTLIA   &     -- &     -- &    728 &   728 \\
    AUFLIA     &      4 &      4 &      4 &     4 \\
    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
    BV         &     85 &     85 &   5151 &  5751 \\
    BVFP       &     -- &     -- &     24 &    24 \\
    FP         &     -- &     -- &     61 &    61 \\
    LIA        &    201 &    201 &    388 &   388 \\
    LRA        &    339 &    339 &   2419 &  2419 \\
    NIA        &      9 &      9 &     14 &    14 \\
    NRA        &   3788 &   3788 &   3811 &  3813 \\
    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
    QF\_ALIA   &    134 &    139 &    139 &   139 \\
    QF\_ANIA   &      6 &      8 &      8 &     8 \\
    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
    QF\_AX     &    551 &    551 &    551 &   551 \\
    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
    QF\_DT     &     -- &     -- &   8000 &  8000 \\
    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
    QF\_LIRA   &      6 &      6 &      7 &     7 \\
    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
    QF\_NIRA   &      2 &      2 &      3 &     3 \\
    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
    QF\_RDL    &    220 &    220 &    255 &   255 \\
    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
    UF         &   2839 &   2839 &   7562 &  7562 \\
    UFBV       &     71 &     71 &    200 &   200 \\
    UFDT       &     -- &     -- &   4535 &  4527 \\
    UFDTLIA    &     -- &     -- &    303 &   303 \\
    UFIDL      &     68 &     68 &     68 &    68 \\
    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
    UFLRA      &     25 &     25 &     15 &    15 \\
    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
    \hline
    Total      & 154238 & 154424 & 256973 & 333241 \\
    \hline
  \end{tabular}}
\end{table}

@@

\TODO: explain those aspects of the procedure that are required to
understand the results (e.g., time limits, scoring)
